---
title: "Glossary - Glosario Teaching Teach Together"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(readxl)
library(DT)
GlosarioT3rmd <- read_excel("files/GlosarioT3.xlsx", 
                         sheet = "LexiconTraduccion")
knitr::opts_chunk$set(echo = FALSE)
```


## English

This glossary is from the book [Teaching Teach Together](https://teachtogether.tech/) by Greg Wilson.
During the [translation of the book into Spanish](https://github.com/gvwilson/teachtogether.tech/blob/master/es/README.md), a glossary was prepared in both languages, as well as a list of terms in both languages without definition.

```{r echo=FALSE}
Englishorder <- GlosarioT3rmd %>%
  arrange(term_en) %>%
  mutate(term = term_en, 
         acronym, 
         definition = def_en, 
         reference = paste0(.$ref_en_a,.$ref_en_b)) %>%
  mutate(reference = str_replace_all(.$reference,"NA","")) %>%
  select(term, acronym, definition, reference)

datatable(Englishorder)
```

## Español

Este glosario corresponde al libro [Teaching Teach Together](https://teachtogether.tech/) de Greg Wilson.
Durante la [traducción del libro al español](https://github.com/gvwilson/teachtogether.tech/blob/master/es/README.md) se armó un glosario en ambos idiomas, además de un listado de términos (sin definición) en ambos idiomas.

```{r echo=FALSE}
Spanishorder <- GlosarioT3rmd %>%
  arrange(term_es) %>%
  mutate(termino = term_es, 
         acronimo = acronym, 
         definicion = def_es, 
         referencias = paste0(.$ref_es_a,.$ref_es_b)) %>%
  mutate(referencias = str_replace_all(.$referencias,"NA","")) %>%
  select(termino, acronimo, definicion, referencias)

datatable(Spanishorder)
```

## Inglés-Español | English-Spanish

List of Spanish-English and English-Spanish terms.
Listado de términos Español-Inglés e Inglés-Español.

```{r echo=FALSE}
both_languages <- GlosarioT3rmd %>%
  arrange(term_en) %>%
  mutate(English = term_en, 
         Spanish = term_es, 
         Acronym = acronym) %>%
  select(English, Spanish, Acronym)

datatable(both_languages)
```
